From Object Classification to Naming:\\ Modeling Entry-level Names for Real-world Objects

### 2019-12-10 papers/ACL2020/analysis.tex
pass over sect 5

The previous Section \ref{sec:experiments} looked at the performance of the different naming models using vanilla evaluation methods like accuracy.
This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
In the following, we use our verification data to assess the severity of errors in different naming models.

\paragraph{Error Categories} We categorize model predictions into several types (see also Figure~\ref{fig:mistakes} for examples).
Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a random name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}

\begin{tabularx}{.46\textwidth}{@{~}lX}
	\textbf{\sameobject:} & alternative name for the same object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
	\textbf{LowCount:} & name produced by 1 annotator\\
	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})\\
\end{tabularx}

Semantically related names are determined with WordNet \cite{fellbaum1998wordnet}. 
%\iffalse
%\begin{itemize}
%	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
%	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
%	\item LowCount: a name produced by only one annotator
%	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
%\end{itemize}
%\fi

@@

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. 
The proportion of the human-like errors that related inadequate alternatives is surprisingly constant across all models.
Both object detection models achieve essentially the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
However, it also predicts fewer valid alternatives (SameObject).
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related'' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.

@@

\paragraph{Low Human Agreement, Worse Predictions?}
%An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
%This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.

Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more or less than 90\% of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\

>>>>

The previous section looked at the performance of the different naming models using a standard single-label evaluation scheme.
%vanilla evaluation methods like accuracy.
This way of evaluating object naming is unsatisfactory: the \mn data, and the verification data, clearly shows that other names than the entry-level name may be adequate too. 
In the following, we use our verification data to assess the severity of errors in different naming models.

\paragraph{Error Categories} We categorize model predictions into the following types (see also Figure~\ref{fig:mistakes} for examples).
Besides \textit{Hit} (the entry-level name) and \textit{Off} (none of the following categories, representing a wrong name), we distinguish between different \textit{Human-like mishits}:\\\vspace{-2ex}

\begin{tabularx}{.46\textwidth}{@{~}lX}
	\textbf{\sameobject:} & alternative name for the same object, estimated from \mn and including WordNet synonyms and hypernyms (\name{house/building}; \citealt{fellbaum1998wordnet}). \\
%(see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building}) \\
	\textbf{OtherObject:} & name produced by annotators, but not an alternative of the entry-level name \\
	\textbf{LowCount:} & name produced by 1 annotator\\
	\textbf{Related:}& a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt}; also estimated from WordNet)\\
\end{tabularx}

%Semantically related names are determined with WordNet 
%\iffalse
%\begin{itemize}
%	\item \sameobject: an alternative name for the object (see Section~\ref{sect:mn_verification}), or a synonym or a hypernym (\name{house/building})
%	\item OtherObject: a name produced by annotators, but not an alternative of the entry-level name 
%	\item LowCount: a name produced by only one annotator
%	\item Related: a hyponym or co-hyponym of the entry-level (\textit{jacket/shirt})
%\end{itemize}
%\fi

@@

Table \ref{tab:humanlike} shows the breakdown of the results for the error categories explained above. 
The proportion of the human-like errors that related inadequate alternatives is surprisingly constant across all models.
Both object detection models achieve essentially the same portion of human-like mishits. Thus, the main difference of FRCNN$_{\text{MN442}}$ to  FRCNN$_{\text{VG1600}}$ is that the former makes more nonsensical errors (column Off), which might be an effect of the reduction in training data.
Importantly, the transferred classification model FRCNN$_{\text{VG1600--VGMN}}$ achieves more hits and also fewer nonsensical errors (other) compared to FRCNN$_{\text{VG1600}}$.
However, it also predicts fewer valid alternatives (SameObject).
This suggests that the transfer learning approach is most effective when the object detection model achieves a valid prediction, which is then calibrated to a perfect hit (it predicts the entry-level) by the fine-tuned classification model.
The proportion of instances for which the ResNet models predict a `related' category is high, which suggests that they tend to confuse invalid names that are semantically similar to a valid name.

@@

\paragraph{Low Human Agreement, Worse Predictions}
%An important observation in Section \ref{sec:manynames} is that even the high number of annotations for an object in ManyNames might not be enough to be fully confident about the entry-level name.
%This suggests that there is a certain portion of objects in the dataset that could be difficult to name even for humans, e.g.,~for linguistic reasons (they don't know how to name the object adequately), or whose name depends on the speaker's interpretation of the situation in which the object is shown, such that an agreement on a certain name is difficult to achieve.

Table \ref{tab:exp_errors_agreement} shows a break-down of model predictions and errors for objects with high and low naming agreement in ManyNames, i.e.\ objects where more (viz.\ less) than 90\% of the annotators opted for the entry-level name. 
Here, we generally find that for all models the portion of hits is extremely high when human agreement is also high.
Note that this holds even for the ResNet-based classifiers that generally achieve lower accuracy.
When human agreement is lower, all models produce fewer hits and more valid alternatives, indicating a similarity between what is difficult for models and humans.
%Interestingly, also the portion of incorrect predictions is substantially higher when the agreement is lower. % \sz{why???}\\
